Adopting agile in the large: motivations, success factors and challenges

### 2014-05-11 journal/article.tex
Work in progress

"C: Adapting non-development parts of organization to agile"

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MARKETING NEEDS TO KNOW ON BEFOREHAND WHAT WILL BE RELEASED
% 
% 
% * Problem: Teams completed backlog --> Continued with stories direct from customer --> Single customer bias
% * Problem: Sales and marketing organization had a different vision of the product
% * Problem: Product marketing was not collaborative, and in old mindset
% * Problem: Requirements --> user stories more granular and prioritized
% [P31]
% After several months of working on the new products, the Agile teams “drained”
% the backlog.   For a while, they kept busy working on new user stories that came
% directly from the strategic customer.  This began to lead to a disconnect
% between what the marketing and sales organizations believed to be the overall
% direction of the product, and the actual direction it was taking based on the
% needs of a single customer. It was clearly time for a regroup, and the
% engineering team pushed back on the MRD.  They were in full production mode
% using Agile and they needed more granular, prioritized user stories to fuel
% their efforts.  The teams needed product marketing to be more collaborative in
% the decomposition of the requirements. This was a totally foreign concept for
% the product marketing team. They had approached the relationship with
% engineering as a “black box” – high level requirements went in, and something
% eventually came out (usually late, and sometimes off the mark on what they
% expected).
% 
% 
% * Challenge: Accomodate time for export clearance
% * Challenge: Acquire third-party licensing authority --> prior to product release
% * Challenge: These processes will remain traditional
% * Challenge: Marketing needs some lead time
% * Enablement activities (sales materials, training)
% * These steps take time, but they are part of the product lifecycle
% * Challenge: Must know beforehand what will be in the product
% [P31]
% While changing our process in the front end of the value chain began to yield
% success, we discovered that there was also a traditional wall at the back end:
% our product release process.
% While the Agile approach enables teams to be flexible with regard to
% prioritization, and very adaptive to changing market conditions and customer
% needs, there are certain “laws of physics” required to release commercial
% product that cannot be altered. For example, the time required to acquire export
% clearance or to acquire third-party licensing authority prior to product
% release.  As a vendor that makes products that must be marketed, sold and
% implemented, there are several traditional processes that are involved in
% releasing our products to market.
% 
% First there are the regulatory requirements such as export compliance relative
% to exporting code with certain levels of encryption,  then there are the
% marketing launch plans (demand generation campaigns, collateral, Web site,
% public relations), and finally, the field enablement activities (sales
% materials, training).  All these initiatives take time, and they cannot begin
% without knowledge of exactly what is going to be in the product.
% 
% 
% * Problem: Marketing had to know on beforehand what will be in the release
% * Problem: Business went with requiring a fixed delivery date and a fixed feature set
% [P31]
% Serious friction arose. The development teams became frustrated because they
% felt marketing and the NPI process was stalling their progress and throwing up
% barriers against the core principles they had adopted.  Marketing, who needed to
% begin prepping for the launch of the product about three months before the
% actual date, found themselves struggling to message and develop materials and
% campaigns without a clear understanding of the features and functionality that
% would actually be “ready” on the release date. And, the NPI group could not
% apply for export compliance nor could they request any third party license
% authorization without knowing what was actually going to be in the product.
% 
% 
% * Solution: Development and product marketing work together
% * Solution: Product marketing can require a release to be completed in 90 days
% [P31]
% What we instituted was what we call an “Iron Triangle.” The concept is that at
% some number of sprints out before a release, we would commit to delivering a
% fixed set of features and functionality  at a certain date.  Of course, there
% was always the opportunity for us to deliver more than what we committed to, 
% but we absolutely had to deliver the set features by the set date.
% 
% If  product marketing wants to release product for any reason they can “declare”
% a release date, and  we’re able to lock the current feature set and have  the
% code ready to release within two sprints of the date they declare the release
% necessary.

>>>>

"C: Difficulties with requirements engineering or backlog"
______________________________________________________________________

P 1: Abdelnour-Nocera 2007 - Adopting Agile in a large organization - balancing the old with the new.pdf - 1:13 [Extracting user stories from e..]  (10:1790-10:2192)   (Super)
Codes:	[C: Adapting non-development parts of organization to agile - Family: RQ3: Challenges] [C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

Extracting user stories from existing, very detailed ‘marketing requirements 
documents’ (MRDs) was another workaround. These MRDs were a prominent artifact 
found across the organization. Leaders of Project Z claimed that it was very difficult 
to work with such detailed documents in a project whose scope could change rapidly; 
one Agile developer described MRDs as “not based in reality at all”.

P 2: Abdelnour-Nocera 2008 - Adopting Agile In A Large Organisation.pdf - 2:20 [Extracting user stories from e..]  (9:389-9:791)   (Super)
Codes:	[C: Adapting non-development parts of organization to agile - Family: RQ3: Challenges] [C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

Extracting user stories from existing, very detailed ‘marketing requirements 
documents’ (MRDs) was another workaround. These MRDs were a prominent artifact 
found across the organisation. Leaders of Project Z claimed that it was very difficult 
to work with such detailed documents in a project whose scope could change rapidly; 
one agile developer described MRDs as “not based in reality at all”.

Comment:
The problem with MRDs is a symptom of the challenge to integrate "the business" with the agile process.

P 5: Beavers 2007 - Managing A Large 'Agile' Software Engineering Organization.pdf - 5:32 [There was constant debate over..]  (5:2150-5:2761)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

There was 
constant debate over both the meaning of the 
requirement and whether or not the requirement was 
met.  Quality Assurance engineers were frustrated 
trying to determine whether or not we should accept 
this feature.  Simply put, we had not invested enough 
of our velocity in either up front or ongoing 
requirements elaboration.
Going into the second release, we knew we had to 
do a better job with managing, elaborating, and 
prioritizing requirements.  This had strictly been an 
issue regarding where we chose to invest our energy.  
Properly managing requirements was critical.

P11: Cowan 2011 - When The VP Is A Scrum Master, You Hit The Ground Running.pdf - 11:31 [Writing and grooming user stor..]  (4:974-4:2298)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

Writing and 
grooming user stories seems like a simple process during 
Scrum training.  When many teams start sprinting at once, no 
one starts off as an expert at writing stories.  In the mad rush to 
convert requirements to stories, many stories had the correct 
format, but were often too big, too ambiguous, or too 
prescriptive.  Product owners and teams who held grooming 
sessions once or twice a week over time refined their backlogs 
so that planning meetings were short, and there was no wasted 
time between sprints trying to figure out what to do next.  For 
one untended product backlog, we instituted “speed grooming” 
where we spent a maximum of five minutes discussing a story 
to categorize it as “ready for a team,” “obsolete,” “more 
grooming,” etc., so the stories could be readied for upcoming 
sprints.  Most of our stories were for system software, not end 
user features, so teams consistently underestimated how long a 
story would take, and would complain that it couldn’t be 
broken down further.  All of sudden they were being required 
to break down work that used to take months into tasks of a 
few hours.  In hindsight, we could have reduced stress on 
everyone if we had devoted more time upfront to developing 
everyone’s skills in writing stories and decomposing epics.

P17: Gat 2006 - How BMC is Scaling Agile Development.pdf - 17:18 [As BMC went through their init..]  (4:45-4:850)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

As BMC went through their initial iterations, they
realized there was often a gap between the level of
detail in their system level features and the detail
needed for iteration planning and execution. The use of
simple “throw away stories” was insufficient to their
challenge of scale. To bridge this gap, BMC created
the role of Requirements Architect as part of each
development team.
The responsibility of each Requirements Architect
is to take the high-level features defined by product
management and decompose these on a just-in-time
basis into the more detailed requirements and stories
needed to drive iteration planning and development.
This new role increased the accuracy of development
estimates and improved the collaboration between the
development team and product management.

P17: Gat 2006 - How BMC is Scaling Agile Development.pdf - 17:29 [One of the challenges BMC face..]  (6:138-6:450)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

One of the challenges BMC faces is defining the right
level of requirement detail at the right time in the life
cycle. BMC is now using Rally Software to manage a
prioritized feature backlog and to elaborate the
requirements and stories for each component that will
likely be needed to implement the feature.

P24: Hansen 2009 - From Cmmi And Isolation To Scrum, Agile, Lean And Collaboration.pdf - 24:13 [Initially we started with the ..]  (3:3312-3:3922)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] [S: Pay attention to the product owner role - Family: RQ4: Success factors] 
No memos

Initially we started with the Product Owner (PO) 
as a role for sales and account management. It worked 
reasonably well with local teams in Denmark when 
they could collaborate and meet when required. But it 
did not work well with teams in Bangladesh. We 
moved some of the very experienced senior developers 
and consultants into global PO roles to establish a more 
structured flow of tasks and collaboration with the 
teams.  
To establish a structure to improve the flow of 
work between the Danish and the Bangladeshi teams 
we introduced a “Proxy PO” for each team in 
Bangladesh (figure 3).

P24: Hansen 2009 - From Cmmi And Isolation To Scrum, Agile, Lean And Collaboration.pdf - 24:14 [Understanding the problem doma..]  (3:4124-4:62)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

Understanding the problem domain and how the 
different requirements were related was still hard. We 
used many different techniques to move the domain 
285knowledge and user understanding out to the different 
teams.

P24: Hansen 2009 - From Cmmi And Isolation To Scrum, Agile, Lean And Collaboration.pdf - 24:20 [Global planning Having one tea..]  (4:2827-4:3579)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

Global planning 
Having one team and therefore one sprint backlog 
meant, that we had to do sprint planning together. Not 
an easy task, but after some experiments, we came up 
with a solution that worked for us: 
• The whole global team was presented with the user 
stories online 
• The global team went offline and started to break 
down the stories and meet to synchronize sprint 
backlog items into one sprint backlog 
• The global team informed the PO of the result 
We spent a lot of time trying to make it work well, 
and it required a high level of trust between all parties.  
It also required a lot of knowledge of the business 
domain, but made it easy to ask for the relevant 
knowledge when doing the breakdown and planning.

P24: Hansen 2009 - From Cmmi And Isolation To Scrum, Agile, Lean And Collaboration.pdf - 24:22 [The R&D team could build the b..]  (5:3659-5:4291)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

The R&D team could build the best quality code, 
but we kept building elements of the wrong things. It 
was almost like building a top of the line V12 engine, 
for a solar cell car race. The trust between the team and 
the PO were at stake. “I told you to build an engine, 
and you should have known it was an electric engine I 
needed”. So once again we had to improve the quality 
and understanding of requirements between the PO and 
the global team both before and during the actual 
development in the sprint. After retrospectives and 
more discussions, we decided to try moving the PO 
into the Danish R&D team room.

P27: Lee 2008 - Forming To Performing - Transitioning Large-Scale Project Into Agile.pdf - 27:19 [The team had difficulty estima..]  (3:567-3:858)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

The team had difficulty
estimating tasks during the planning session: What
should go into a story? How should a task card be
written? Is the story points system better than the
hour’s system? We also had a lack of well-defined
acceptance criteria before and during the planning
session.

P27: Lee 2008 - Forming To Performing - Transitioning Large-Scale Project Into Agile.pdf - 27:21 [One solution we came up with w..]  (3:2624-3:3190)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

One solution we came up with was to improve the
relationship between us and our internal customers.
Planning sessions were dreaded - long and not well
structured. Our team was driven based on the internal
customer requirements, which went into a backlog
that the program manager also known as Susha
[3]
maintained. The more efficient way to understand
what a task entailed was to involve the customers in
our planning meeting and pair up with them on
writing the actual story. The customers partnered up
with us for 15 minutes during the planning sessions.

P30: Long 2008 - Agile Supports Improved Culture And Quality For Healthwise.pdf - 30:11 [The introduction of Agile rais..]  (3:35-3:514)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

The introduction of Agile raised visibility of the 
requirements churn and lack of clarity in feature 
definition, but writing good user stories remained 
difficult, due in part to the separation between the 
client and product development teams. 
Engineering became known as the “story-eating 
engine.” Stories were being completed, but did 
not always add value for clients.  
Agile successfully exposed the next areas needing 
attention: defining value-added stories.

P30: Long 2008 - Agile Supports Improved Culture And Quality For Healthwise.pdf - 30:38 [Managing an effective enterpri..]  (6:1506-6:1546)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

Managing an effective enterprise backlog.

P31: Maples 2009 - Enterprise Agile Transformation - The Two-Year Wall.pdf - 31:5 [we discovered some areas that ..]  (2:1586-2:1895)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] [C: Problems with separate non-agile QA - Family: RQ3: Challenges] 
No memos

we discovered some areas that 
would require us to adapt our chosen Scrum 
methodology to account for the realities of complex, 
large-scale development.  Two key activities fell 
outside the scope of our original Scrum framework 1. 
Informing how things get into the backlog, and 2. 
Enterprise testing.

P31: Maples 2009 - Enterprise Agile Transformation - The Two-Year Wall.pdf - 31:6 [Once the organization began to..]  (2:2602-2:3650)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

Once the organization began to understand the 
increased productivity of the Agile teams, and they saw 
that every three weeks the teams selected what they 
would work on, they began to grasp the possibility that 
any feature request could be delivered in mere weeks.  
And, suddenly, we found the backlog was “up for 
grabs” at the beginning of each sprint. 
Requests came flooding in from the field, from 
marketing, from our support organization. They would 
be automatically added to the backlog, and each sprint 
became an opportunity to evaluate and reprioritize. 
And, since the Agile approach increases collaboration, 
everyone had the opportunity to “lobby” for his or her 
requests to make the backlog. This constant influx of 
demand from several sources began to put a strain on 
the system.  Questions about how to prioritize the 
backlog items and a subversive process of “backlog 
bartering” began. This negatively impacted the teams 
and their performance, and it also generated distrust 
among the various groups.

P31: Maples 2009 - Enterprise Agile Transformation - The Two-Year Wall.pdf - 31:11 [After several months of workin..]  (4:1-4:1041)   (Super)
Codes:	[C: Adapting non-development parts of organization to agile - Family: RQ3: Challenges] [C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

After several months of working on the new 
products, the Agile teams “drained” the backlog.   For 
a while, they kept busy working on new user stories 
that came directly from the strategic customer.  This 
began to lead to a disconnect between what the 
marketing and sales organizations believed to be the 
overall direction of the product, and the actual direction 
it was taking based on the needs of a single customer.   
It was clearly time for a regroup, and the 
engineering team pushed back on the MRD.  They 
were in full production mode using Agile and they 
needed more granular, prioritized user stories to fuel 
their efforts.  The teams needed product marketing to 
be more collaborative in the decomposition of the 
requirements. This was a totally foreign concept for the 
product marketing team.  They had approached the 
relationship with engineering as a “black box” – highlevel requirements went in, and something eventually 
came out (usually late, and sometimes off the mark on 
what they expected).

P33: Mencke 2008 - A Product Manager'S Guide To Surviving The Big Bang Approach To Agile Transitions.pdf - 33:7 [In addition to the hottest ide..]  (3:634-3:1384)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

In addition to the hottest ideas coming off 
the IdeaExchange, salesforce.com’s product 
managers also have backlogs of important 
features, and these product backlogs are an 
integral part of ADM.
The initial creation and prioritization of 
product backlogs was an ominous challenge, and 
nearly impossible to achieve in the two-month 
timeframe the  product managers were allotted. 
Breaking down requirements into both epic and 
detailed user stories was arduous, and the way in 
which the requirements were broken down was
inconsistent between teams because each team 
had limited insight into how other teams were 
organizing their product backlogs. 
To address this issue, salesforce.com built 
an in-house app called  Scrumforce

P33: Mencke 2008 - A Product Manager'S Guide To Surviving The Big Bang Approach To Agile Transitions.pdf - 33:10 [The transition from writing fu..]  (4:786-4:979)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

The transition from writing full 
product or functional specs to writing user 
stories is challenging. Learn how to break up 
larger features into smaller user stories, and 
prioritize them.

P33: Mencke 2008 - A Product Manager'S Guide To Surviving The Big Bang Approach To Agile Transitions.pdf - 33:11 [With user stories come smaller..]  (4:1058-4:1661)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] [S: Requirements engineering is implemented correctly - Family: RQ4: Success factors] 
No memos

With user stories come smaller and more 
vague requirements, and because of the agile 
nature of the development process, the 
product owner has a tendency to change 
requirements during a sprint. Often, this is 
due to the product owner not specifying the 
full requirements before the sprint starts. 
This can waste  time and result in work that 
is thrown away. User stories should be 
complete, have acceptance criteria, and be 
usability tested before being added to a 
sprint. Having clear guidelines prepared for 
when the team is ready to tackle a user story 
will help reduce waste.

P37: O'Connor 2010 - Letters from the Edge of an Agile Transition.pdf - 37:22 [Our business analysts were run..]  (4:952-4:1713)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

Our business analysts were running into
the same issue one level up. They were not used to providing
feature requirements in story form, much less breaking down
these ”feature” level stories into stories that could be reasonably estimated by the development team. I realized almost
immediately the stories were too big, but you can’t force immediate understanding. Like any skill, estimating takes practice. We went through many agonizing estimation and story
breakdown sessions before we started to get some traction.
As we began to build up some historical data this closed the
feedback loop. The team was able to see that we were frequently underestimating and that this was directly connected
to the trouble we were still having with story breakdown.

P37: O'Connor 2010 - Letters from the Edge of an Agile Transition.pdf - 37:27 [We started ?nishing cards, but..]  (4:4347-4:4838)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

We started ﬁnishing cards,
but found that estimates of hours often took weeks. Stories
would spawn additional stories in order to reach completion. For example, a story that started with a two day estimate would generate a week’s worth of stories (sometimes
even more than a week!). Many agile developers would say
”Great! That’s part of agile.” Gaining clarity on a story and
understanding that there is more to it is part of the process. Unfortunately this was happening far too often.

P39: Prokhorenko 2012 - Skiing And Boxing - Coaching Product And Enterprise Teams.pdf - 39:19 [there were a number of difficu..]  (3:3675-3:4041)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

there were a number of difficulties in 
requirements management. Actual stakeholders weren’t 
available for the teams due to  many reasons and they used 
another consulting company in the UK to gather their 
requirements, design UI and communicate them back to teams. 
Even more requirements were provided from risk management 
subject matter experts in London.

Comment:
This sounds a bit like the initial state.

P39: Prokhorenko 2012 - Skiing And Boxing - Coaching Product And Enterprise Teams.pdf - 39:31 [Product discovery workshops ar..]  (6:2221-6:2778)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

Product discovery workshops are an extremely efficient 
technique allowing for quick elaboration of a product roadmap 
and creating mid-term requirements details. However, as most 
efficient tools do, it has certain limitations. One of them is the 
need to have the PO and the team co-located for a sprint which 
might be a budget issue for a distributed project. Another one is 
the nature of a PO role in enterprise projects where you simply 
can’t bring all the subject matter experts in one place with the 
team for any reasonable amount of time.

P45: Schnitter 2011 - Large-Scale Agile Software Development At Sap Ag.pdf - 45:20 [Around the same time some prob..]  (5:998-5:2037)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

Around the same time some problems surfaced which were not connected to Scrum
usage but needed to be resolved before moving to Scrum on a large scale:
1. Communication among product management, software architects, development
teams, and quality assurance was not strong enough to ensure a common understanding of development goals. Product management often was unable to communicate product requirements to software engineers. Languages and notations differed signiﬁcantly.
2. The role of software architecture (high-level design) was not yet well understood.
This led to increased dependencies among products and components, e. g. because
componentization was weak and code reuse was highly valued. Another result was
the lack of conceptual preparation for the development teams for whom there were
too many obstacles to harmonize on interfaces and adhere to delivery timelines.
To overcome both problems a team was formed to provide education on software architecture for developers, software architects, and product management.

P45: Schnitter 2011 - Large-Scale Agile Software Development At Sap Ag.pdf - 45:35 [Upscaling methods were mainly ..]  (9:1718-9:2252)   (Super)
Codes:	[C: Adapting non-development parts of organization to agile - Family: RQ3: Challenges] [C: Agile by the book is not good enough (no exact recipes) - Family: RQ3: Challenges] [C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

Upscaling methods were mainly driven by theoretical considerations. Implementing
themrevealedthatthe skills andknowledge ofproductmanagers and software architects
were often not sufﬁcient to manage a number of Scrum teams concurrently. Product
teams had to communicate with business management, marketing, and ﬁeld services
who were not fully prepared for how Scrum and the product teams’ expectations would
change their daily work. The process of software requirements engineering were found
to require a major adjustment.

P45: Schnitter 2011 - Large-Scale Agile Software Development At Sap Ag.pdf - 45:39 [A three-level hierarchy ofteam..]  (10:1787-10:2327)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] [T: Impact on organization - Family: RQ2: Transformation process] 
No memos

A three-level hierarchy ofteams to manage requirements for product backlog generation has not yet proven to work as expected. Currently the high complexity of SAP’s
products which is reﬂected in the organizational structure of SAP’s development areas
makes it impossible to drop one hierarchy level of project management. This observation has triggered signiﬁcant effort to rigorously break up SAP’s product lines into
separate components to ensure that no product component needs more resources than
the 130 people as calculated above.

P46: Seffernick 2007 - Enabling Agile In A Large Organization Our Journey Down The Yellow Brick Road.pdf - 46:34 [After month 16 of our journey,..]  (3:3987-3:4981)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] [C: Mapping agile to match the old model - Family: RQ3: Challenges] [I: Training - Family: Investing in change] [S: Emphasize principles instead of mechanics - Family: RQ4: Success factors] [S: Pay attention to the product owner role - Family: RQ4: Success factors] 
No memos

After month 16 of our journey, focus shifted 
toward connecting the product owners, ScrumMasters 
and technology managers prior to the project start. Our 
projects were starting without good backlogs and the 
level of product owner involvement was inconsistent, 
causing projects to start slowly. After some soul 
searching we concluded that we were treating agile 
development as a paradigm shift (mapping existing 
roles to Scrum roles, yet not doing anything different). 
What we needed was to educate it as a new paradigm. 
The result was Agile Connections. This is a sequence 
of training that starts with an overview to create 
awareness and desire to use agile practices in 
delivering the business value. Then, hands-on 
workshops transfer knowledge, followed by jump 
starts and coaching to help reinforce the ability to use 
the practices. The overall goal is to get the product 
owner, ScrumMaster and technology manager together 
to enable projects to start better.

P48: Smits 2011 - Agile Experience Report - Transition And Complexity At Cisco Voice Technology Group.pdf - 48:31 [An executive Portfolio Investm..]  (4:2117-4:2972)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

An executive Portfolio Investment Committee was 
initiated with the goal of working across all of the 
business units in our Technology Group to set 
investment priorities. Two problems emerged – we 
did not have the management information to support 
the decisions of the Portfolio Committee, and 
information about the strategic decisions and 
direction were not effectively communicated to the 
organization so that all participants in the system 
release planning process were informed. The next 
stage of “decomposition” of Themes, Epics and User 
Stories didn’t really happen, so that the chunks of 
work were so large that the Product Teams and 
Scrum teams had to spend an inordinate amount of 
time breaking things down, (and clarifying the 
requirements at the lower levels) before any sprint 
zero or sprint planning could occur.

P51: Vlaanderen 2012 - Growing Into Agility - Process Implementation Paths For Scrum.pdf - 51:13 [The sprint planning meeting in..]  (5:720-5:1333)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

The sprint planning meeting initially took approximately one day, because
all the user stories had to be discussed, estimated and planned at once. This
was considered too long to be eﬀective. Therefore, story estimation is now done
regularly throughout the sprints. This requires shorter bursts of attention, which
eases the process. On the day of the sprint planning, the product owners present
the user stories to their own team(s), followed by the selection and planning of
user stories by the development teams. The process of selection and planning
now takes approximately one hour, instead of one day.

P51: Vlaanderen 2012 - Growing Into Agility - Process Implementation Paths For Scrum.pdf - 51:26 [Until 2007, agile product deve..]  (6:2886-7:730)   (Super)
Codes:	[C: Difficulties with requirements engineering or backlog - Family: RQ3: Challenges] 
No memos

Until 2007, agile product development was accompanied by
non-agile product management. Although several stages of elaboration were employed, no ﬁxed cycles were used. This caused that product managers did not
manage to provide development with suﬃciently detailed requirements before122 K. Vlaanderen et al.
the start of each sprint. To improve this, the product management team adjusted their process to the Scrum principles as well. This implied a continuous
adaptation of the product backlog to a changing environment. Since Scrum itself does not provide guidelines for eﬀectively managing large amounts of requirements of diﬀerent granularity, a set of stages has been introduced, called
the Agile Requirements Reﬁnery [26]. Within the agile requirements reﬁnery, an
idea will generally move through the stages vision, theme, concept, and requirement deﬁnition. During these stages, requirements are reﬁned with details and
speciﬁcations. This has resulted in a new categorization on the product backlog.
